An Audio-Based 3D Spatial Guidance AR System for Blind Users

### 2020-06-17 manuscript.tex
Updates from Overleaf

\documentclass[runningheads]{res/templates/llncs}
%
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[hyphens]{url}
\usepackage{hyperref}

@@

\title{An Audio-Based 3D Spatial Guidance AR System for Blind Users\thanks{JMC, BB and HS were supported by NIH grant 5R01EY025332 and NIDILRR grant 90RE5024-01-00. We thank Dr. Roberto Manduchi, Dr. Natela Shanidze, Dr. Santani Teng and Dr. Ali Cheraghi for helpful suggestions about the experiments.}}

@@

We build on our past work on CamIO
\cite{shenCamIO3DComputer2013,coughlanEvaluatingAuthorUser2017,coughlanTowardsAccessibleAudioLabeling2020},
which is short for ``Camera Input-Output.'' We have implemented CamIO as
a stand-alone iPhone app that tracks an inexpensive wooden stylus held
by the user to point at locations of interest on an object (called
hotspots). When the user points at a hotspot with the stylus tip,
relevant audio information, such as text-to-speech or other sounds, is
announced.

@@

Guidance not only saves the user time in exploring large or intricate
objects, or objects lacking in tactile features, but can enable entirely
new ways of interacting with objects. For instance, a geography learning
app could ask a student to point to a specific city on a world globe,
and if the student has trouble finding it, the app could guide them to
it in an intuitive way. Other examples could include guiding a user to a
specific button on an appliance (such as a microwave) to perform a
desired function, guiding a student to a specific element on the
periodic table, or even guiding a repairperson to find a part of a
machine with limited visibility. Our guidance system is inspired by
recent work on auditory and haptic displays for 3D spatial guidance
\cite{mayAuditoryDisplaysFacilitate2019,guezou-philippePrototypingEvaluatingSensory2018},
which provide real-time audio/haptic feedback to guide a user towards a
target in a virtual environment. We initially developed an interface
similar to \cite{mayAuditoryDisplaysFacilitate2019} for CamIO, but after
preliminary testing we devised a simpler and more effective interface
for our application, which we evaluated experimentally with four blind
participants.

@@

CamIO is an augmented reality (AR) iPhone app that uses computer vision
to provide audio labels for rigid 3D objects. The rigid object of
interest is mounted on a board, which is a printed barcode pattern
(Fig. \ref{fig:exp}) that allows CamIO to estimate the object's pose (3D
translation and 3D orientation) relative to the camera. The iPhone is
typically mounted on a tripod or a gooseneck cellphone holder
Fig. ref{fig:exp} to obtain a clear view of the board and object, but in
some cases \cite{coughlanTowardsAccessibleAudioLabeling2020} users may
hold the iPhone by hand. The user points the tip of a passive wooden
stylus Fig. \ref{fig:exp}, covered with another barcode pattern, to different
locations on an object. CamIO estimates the stylus tip's 3D location
relative to the camera and uses the pose estimate of the board to
determine the stylus tip's 3D location relative to the object. Whenever
the tip is close enough to a pre-defined hotspot, it triggers audio
information about the hotspot. (In other words, hotspot locations are
defined relative to the board, which is mounted rigidly to the object.)

A second stylus (not shown, identical in form but distinct from the one
shown in Fig. \ref{fig:exp}) is used to create new hotspots, and allows the
user to make an audio recording to associate with each new hotspot. Our
recent work \cite{coughlanTowardsAccessibleAudioLabeling2020}
demonstrates the accessibility of this authoring process, which allows
blind users to create their own annotations (hotspots and associated
audio labels) independently. However, in the study presented in this
paper, the experimenter was the only one who created hotspots, since the
emphasis here is on providing guidance to pre-existing hotspots.

@@

Informal tests with two blind participants (one female of age 42, who is
also participant P1 in the experiment described in the next section, and
one male of age 73) showed that this guidance worked satisfactorily in
some cases. However, we found that the feedback was too indirect: the
participants didn't always know how to move the stylus to increase the
tempo. As a result, the resulting guidance process was unacceptably
slow. Thus we devised a second, more direct guidance approach: verbal
directions telling the user to move the stylus along the cardinal
directions (up, down, left, right, forward or back). While the optimal
direction to move the stylus tip towards the hotspot might entail a
combination of these directions (e.g., simultaneously move left and up),
for simplicity we issue directions along only one cardinal direction at
a time -- the direction that will most improve the alignment to the
target.

We define the guidance interface as follows. The board (barcode pattern
beneath the truck, see Fig. \ref{fig:exp}) defines an xyz coordinate frame,
with \(+x\) = right, \(-x\) = left, \(+y\) = forward (away from the
user), \(-y\) = back (towards the user), \(+z\) = up and \(-z\) = down.
Let the desired target hotspot location be denoted \((x*, y*, z*)\), and
the current location of the stylus tip be \((x,y,z)\). Define the error
vector \(e = (x-x*, y-y*, z-z*)\), and let index \(a = argmax_i |e_i|\),
i.e., a is the index (1, 2 or 3, corresponding to x, y or z,
respectively) of the entry in e with the highest absolute value. In
other words, a indicates which coordinate (x, y or z) is most discrepant
from the target coordinate location \((x*, y*, z*)\). Then the
appropriate direction is issued, e.g., ``left'' if \(a = 1\) and
\(x > x*\), ``right'' if \(a = 1\) and \(x < x*\), ``up'' if \(a = 3\)
and \(z < z*\), etc. Directions are announced roughly twice per second
whenever the stylus is visible. The target hotspot is announced when the
stylus gets to within approximately 1 cm from the hotspot. No audio
feedback is issued when the stylus is not visible.

\hypertarget{exp}{%
\section{Experiment with Blind Participants}\label{exp}}

We conducted an experiment to assess the feasibility of the spatial
guidance feedback and to determine whether the feedback speeds up the
target search. The experiment Fig. \ref{fig:exp} compared how much time a blind participant needed to find hotspots (points of interest) on a 3D
object with spatial guidance vs.~without it. The object was a large toy
fire truck (27 cm x 12 cm x 14 cm), with K=10 distinct hotspot locations
defined in advance. The hotspots were tactilely salient features such as
lights, hooks or other features that protruded from the truck. Some
hotspots were in recessed locations on the truck, such as the shift
stick and steering wheel (Fig. \ref{fig:exp}) in the front cabin, or on the
side of the truck facing away from the participant; these hotspots were
difficult to find and access, whether by fingertip or by stylus. In
fact, the difficulty of accessing such locations highlights an advantage
of the CamIO stylus, whose tip need not be visible to the camera. This
allows the user to explore recessed areas or areas that are otherwise
invisible to the camera.

\begin{figure}
\includegraphics[width=0.55\linewidth]{res/img/fig1a}
\includegraphics[width=0.45\linewidth]{res/img/fig1b} 
\caption{(left) Blind participant uses CamIO to explore a toy fire truck. The participant holds the CamIO stylus (a barcode pattern printed on a square wooden dowel with a pointy tip) to point to possible hotspots on the truck. The truck is glued to the board, a piece of paper with a separate barcode pattern, which is taped to the table. An iPhone 8 running CamIO is held by a gooseneck cellphone holder to capture a view of the truck, board and stylus. (right) Stylus points to steering wheel in the truck cabin. Though the steering wheel is in a recessed location that is not visible to CamIO, the stylus tip location can still be estimated.}
\label{fig:exp}
\end{figure}

Each hotspot location was searched for under two feedback conditions: G
(guidance provided) and NG (no guidance). The participant was given up
to 120 sec to find each hotspot, after which a time-out was declared.
In order to minimize the influence of any possible learning effects,
which could make it easier to find a hotspot the second time it was
searched for, we randomized the sequence of hotspots and alternated
between NG and G trials. This resulted in a sequence of 2K = 20 trials,
starting with an NG trial, the same sequence for each participant.

We had a total of N=4 blind participants in our experiment (2 male/2
female, ages from 26-42). Participants P1, P3 and P4 were already
familiar with the CamIO system (P4 is a co-author of this paper) while
P2 was unfamiliar with it. None of the participants was told the study
design before their trials, and we didn't tell them whether or not any
locations would be repeated in the 20 trials. After obtaining IRB
consent, we reviewed how CamIO works if necessary and demonstrated the
audio guidance feature. The experimenter launched CamIO on an iPhone 8
and positioned it on a gooseneck cellphone holder so that the camera
captured the entire truck and board. Each participant spent a short time
practicing with the guidance feature, with help provided by the
experimenter as needed. (The experimenter chose practice hotspots that
were different from the pre-defined K=10 hotspots.) In the practice
phase, the experimenter explained that barriers sometimes block the user
from moving in the suggested guidance direction. For instance, if in
Fig. \ref{fig:exp} the system directs the participant to move ``forward''
towards the left side mirror, the stylus will soon hit the cabin
roof/wall as it moves towards the mirror; the participant must find ways
around such obstacles to find the target hotspot.

Next each participant performed the formal experimental trials, which
consisted of the 2K=20 trial sequence described above. This sequence
included 10 trials of both conditions (G and NG), for a total of 20
trials per participant. We  placed a visual barrier between the participant and the object while the experimenter defined the hotspot in each trial to prevent participants from using any residual vision to see the location of the hotspot. After completing the 20 search trials, we
administered a System Usability Scale (SUS) \cite{brooke1996sus} to
estimate the usability of the guidance system. Finally, we conducted a
semi-structured interview asking what participants liked and disliked
about the system, what needed to be improved, and how they might
envision an ideal guidance system. Since P4 is a co-author on this
paper, we did not administer the SUS or semi-structured interview to
him.

\hypertarget{results}{%
\section{Experimental Results and Analysis}\label{results}}

We conducted an experiment to assess the feasibility of the spatial
guidance feedback and to determine whether the feedback speeds up the
target search. The experiment (Fig. \ref{fig:exp}) compared how much time a
blind participant needed to find hotspots (points of interest) on a 3D
object with spatial guidance vs.~without it. The object was a large toy
fire truck (27 cm x 12 cm x 14 cm), with K=10 distinct hotspot locations
defined in advance. The hotspots were tactilely salient features such as
lights, hooks or other features that protruded from the truck. Some
hotspots were in recessed locations on the truck, such as the shift
stick and steering wheel (Fig. \ref{fig:exp}) in the front cabin, or on the
side of the truck facing away from the participant; these hotspots were
difficult to find and access, whether by fingertip or by stylus. In
fact, the difficulty of accessing such locations highlights an advantage
of the CamIO stylus, whose tip need not be visible to the camera. This
allows the user to explore recessed areas or areas that are otherwise
invisible to the camera.

\begin{figure}
\includegraphics[width=5.5cm, keepaspectratio,]{res/img/fig2a.jpg}
\includegraphics[width=6.5cm, keepaspectratio,]{res/img/fig2b.jpg}
\caption{(left) Plot of time (x axis) to find target hotspot location for G (‘o’ symbol) vs. NG  (‘x’ symbol) conditions, with time-out declared after 120 sec. of unsuccessful search. Results are shown for each participant (indicated on the y axis and also using color) and at all 10 target locations. (right) Histogram plot showing the distribution of NG time minus G time. The plot aggregates time differences for all participants over all locations; positive times mean the search was faster with G than with NG.}
\label{fig:res}
\end{figure}

We analyzed the differences between times under G vs.~NG using a
Wilcoxon signed rank test. The resulting p-value is p = 3.8 x 10-8. This
is a highly statistically significant p-value supporting the rejection
of the null hypothesis that the distribution of times under G is the
same as the distribution of times under NG.

The following System Usability Scale (SUS) scores were calculated:
P1=65, P2=75, P3=77.5, for an average of 72.5. An SUS score of 68 is
considered ``average'' while scores in the mid- to high 70s are
considered ``good'' (\url{https://measuringu.com/interpret-sus-score/}).
Overall, the SUS scores suggest that the guidance system is usable but
needs improvement.

Next we summarize the qualitative feedback we obtained in the
semi-structured interviews. All participants who provided qualitative
feedback (P1, P2 and P3) acknowledged the benefit of the audio guidance
that was provided, which they found intuitive and clearly superior to
finding hotspots without guidance. However, P1 and P2 felt that the
limited spatial accuracy of the CamIO system was the biggest problem
that needed to be addressed; for instance, in some cases the system
announced the target had been reached even though the stylus tip was
hovering about 1 cm above the truck surface. (This spatial inaccuracy
results from noise in the board pose and stylus tip location estimates.)
P3 expressed frustration with time lag, i.e., the voice feedback tended
to lag behind the current location of the stylus, even when she was
moving the stylus slowly; she also felt that the speed of the repetitive
speech feedback made her feel rushed.

@@

We have devised a 3D spatial guidance system that helps a blind user
find a specific location of interest on an object using CamIO, an
audio-based AR system. The guidance system uses simple verbal commands
(``left''/ ``right''/``up''/etc.) to tell the user which direction to
move the stylus tip. Experiments with four blind participants show that
the guidance system significantly speeds up the search for target
hotspots compared with an exhaustive search. A secondary contribution of
this study is to demonstrate the ability of the CamIO stylus to access
recessed or otherwise obscured locations on an object that are not
themselves visible to the camera.

@@

>>>>

\documentclass[runningheads]{res/templates/llncs}
%
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{draftwatermark}

\SetWatermarkText{Preprint – to be published in ICCHP 2020}
\SetWatermarkColor[gray]{0.5}
\SetWatermarkFontSize{1cm}
\SetWatermarkAngle{90}
\SetWatermarkHorCenter{2cm}

@@

\title{An Audio-Based 3D Spatial Guidance AR System for Blind Users}

@@

We build on our past work on CamIO
\cite{shenCamIO3DComputer2013,coughlanEvaluatingAuthorUser2017,coughlanTowardsAccessibleAudioLabeling2020},
which is short for ``Camera Input-Output.'' We have implemented CamIO as
a stand-alone iPhone app that tracks an inexpensive wooden stylus held
by the user to point at locations of interest on an object (called
{\em hotspots}). When the user points at a hotspot with the stylus tip,
relevant audio information, such as text-to-speech or other sounds, is
announced.

@@

Guidance not only saves the user time in exploring large or intricate objects, or objects lacking in tactile features, but can enable entirely new ways of interacting with objects. 
For instance, a geography learning app could ask a student to point to a specific city on a world globe, and if the student has trouble finding it, the app could guide them to it in an intuitive way. 
Other examples could include guiding a user to a specific button on an appliance (such as a microwave oven) to perform a desired function, guiding a student to a specific element on the periodic table, or even guiding a repair-person to find a part of a machine with limited visibility. 
Our guidance system is inspired by recent work on auditory and haptic displays for 3D spatial guidance \cite{mayAuditoryDisplaysFacilitate2019,guezou-philippePrototypingEvaluatingSensory2018,miesenberger_augmented_2018}, which provide real-time audio/haptic feedback to guide a user towards a target in a virtual environment. 
We initially developed an interface similar to \cite{mayAuditoryDisplaysFacilitate2019} for CamIO, but after preliminary testing we devised a simpler and more effective interface for our application, which we evaluated experimentally with four blind participants.

@@

CamIO is an augmented reality (AR) iPhone app that uses computer vision
to provide audio labels for rigid 3D objects. The rigid object of
interest is mounted on a {\em board}, which is a flat printed barcode pattern
(Fig.~\ref{fig:exp}) that allows CamIO to estimate the object's pose (3D
translation and 3D orientation) relative to the camera. The iPhone is
typically mounted on a tripod or a gooseneck cellphone holder
(Fig.~\ref{fig:exp}(left)) to obtain a clear view of the board and object, but in
some cases \cite{coughlanTowardsAccessibleAudioLabeling2020} users may
hold the iPhone by hand. The user points the tip of a passive wooden
{\em stylus} (Fig.~\ref{fig:exp}), covered with another barcode pattern, to different
locations on an object. CamIO estimates the stylus tip's 3D location
relative to the camera and uses the pose estimate of the board to
determine the stylus tip's 3D location relative to the object. (In other words, hotspot locations are
defined relative to the board, which is mounted rigidly to the object.) Whenever
the tip is close enough to a pre-defined hotspot, it triggers audio
information about the hotspot.

A second stylus (not shown, identical in form but distinct from the one
shown in Fig.~\ref{fig:exp}) is used to create new hotspots, and allows the
user to make an audio recording to associate with each new hotspot. Our
recent work \cite{coughlanTowardsAccessibleAudioLabeling2020}
demonstrates the accessibility of this authoring process, which allows
blind users to create their own annotations (hotspots and associated
audio labels) independently. However, in the study presented in this
paper, the experimenter was the only one who created hotspots, since the
emphasis here is on providing guidance to pre-existing hotspots.

@@

Informal tests with two blind participants (one female of age 42, who is also participant P1 in the experiment described in the next section, and one male of age 73) showed that this guidance worked satisfactorily in some cases. 
However, we found that the feedback was too indirect: the participants didn't always know {\em how} to move the stylus to increase the tempo. 
As a result, the resulting guidance process was unacceptably slow. 
Thus we devised a second, more direct guidance approach: verbal directions telling the user to move the stylus along the cardinal directions (up, down, left, right, forward or back). 
While the optimal direction to move the stylus tip towards the hotspot might entail a combination of these directions (e.g., simultaneously move left and up), for simplicity we issue directions along only {\em one} cardinal direction at a time -- the direction that will most improve the alignment to the target.

We define the guidance interface as follows. The board (barcode pattern beneath the truck, see Fig.~\ref{fig:exp}) defines an xyz coordinate frame, with \(+x\) = right, \(-x\) = left, \(+y\) = forward (away from the user), \(-y\) = back (towards the user), \(+z\) = up and \(-z\) = down.
Let the desired target hotspot location be denoted \((x^*, y^*, z^*)\), and the current location of the stylus tip be \((x,y,z)\). 
Define the error vector \(e = (x-x^*, y-y^*, z-z^*)\), and let index \(a = argmax_i |e_i|\), i.e., $a$ is the index (1, 2 or 3, corresponding to x, y or z, respectively) of the entry in $e$ with the highest absolute value. 
In other words, $a$ indicates which coordinate (x, y or z) is most discrepant from the target coordinate location \((x^*, y^*, z^*)\). 
Then the appropriate direction is issued, e.g., ``left'' if \(a = 1\) and \(x > x^*\), ``right'' if \(a = 1\) and \(x < x^*\), ``up'' if \(a = 3\) and \(z < z^*\), etc. 
Directions are announced roughly twice per second whenever the stylus is visible. The target hotspot is announced when the stylus gets to within approximately 1 cm from the hotspot. 
No audio feedback is issued when the stylus is not visible.

\hypertarget{exp}{%
\section{Methods}\label{exp}}

We conducted an experiment to assess the feasibility of the spatial guidance feedback and to determine whether the feedback speeds up the target search. 
The experiment (see setup in Fig.~\ref{fig:exp} (left)) compared how much time a blind participant needed to find hotspots (points of interest) on a 3D object with spatial guidance vs.~without it. 
The object was a large toy fire truck (27 cm x 12 cm x 14 cm), with K=10 distinct hotspot locations defined in advance. 
The hotspots were tactilely salient features such as lights, hooks or other features that protruded from the truck. 
Some hotspots were in recessed locations on the truck, such as the shift stick and steering wheel (Fig.~\ref{fig:exp} (right)) in the front cabin, or on the side of the truck facing away from the participant; these hotspots were difficult to find and access, whether by fingertip or by stylus. 
In fact, the difficulty of accessing such locations highlights an advantage of the CamIO stylus, whose tip need not be visible to the camera. 
This allows the user to explore recessed areas or areas that are otherwise invisible to the camera.

\begin{figure}
\includegraphics[width=0.58\linewidth,height=4.5cm]{res/img/fig1a}
\includegraphics[width=0.42\linewidth,height=4.5cm]{res/img/fig1b} 
%\includegraphics[height=4.5cm\linewidth]{res/img/fig1a}
%\includegraphics[height=4.5cm\linewidth]{res/img/fig1b} 
\caption{(left) Blind participant uses CamIO to explore a toy fire truck. The participant holds the CamIO {\em stylus} (a barcode pattern printed on a square wooden dowel with a pointy tip) to point to possible hotspots on the truck. The truck is glued to the {\em board} (a piece of paper with a separate barcode pattern), which is taped to the table. An iPhone 8 running CamIO is held by a gooseneck cellphone holder to capture a view of the truck, board and stylus. (right) Stylus points to steering wheel in the truck cabin. Though the steering wheel is in a recessed location that is not visible to CamIO, the stylus tip location can still be estimated.}
\label{fig:exp}
\end{figure}

Each of the 10 hotspots was searched for under both feedback conditions: G (guidance provided) and NG (no guidance). 
In order to minimize the influence of any possible learning effects, which could make it easier to find a hotspot the second time it was searched for, we randomized the sequence of hotspots, and alternated between NG and G trials. With 10 trials in both guidance conditions (G and NG), this resulted in a within-subject factorial design with an identical sequence of $2K = 20$ trials per participant.
The participant was given up to 120 sec. to find each hotspot, after which a time-out was declared.

We had a total of N=4 blind participants in our experiment (2 males/2 females, ages from 26-42).
Participants P1, P3 and P4 were already familiar with the CamIO system (P4 is a co-author of this paper) while P2 was unfamiliar with it. 
None of the participants was told the study design before their trials, and we didn't tell them whether or not any locations would be repeated in the 20 trials.

After obtaining IRB consent, we reviewed how CamIO works if necessary and demonstrated the audio guidance feature. 
The experimenter launched CamIO on an iPhone 8 and positioned it on a gooseneck cellphone holder so that the camera captured the entire truck and board. 
Each participant spent a short time practicing with the guidance feature (on different hotspots than the one used for the evaluation), with help provided by the experimenter as needed.

In the practice phase, the experimenter explained that barriers sometimes block the user from moving in the suggested guidance direction. 
For instance, if in Fig.~\ref{fig:exp}(right) the system directs the participant to move ``forward'' towards the left side mirror, the stylus will soon hit the cabin roof/wall as it moves towards the mirror; the participant must find ways around such obstacles to find the target hotspot.

Next each participant performed the formal experimental trials, which consisted of the 20-trial sequence described above. 
We  placed a visual barrier between the participant and the object while the experimenter defined the hotspot in each trial to prevent participants from using any residual vision to see the location of the hotspot. After completing the 20 search trials, we administered a System Usability Scale (SUS) \cite{brooke1996sus} to estimate the usability of the guidance system. 
Finally, we conducted a semi-structured interview asking what participants liked and disliked about the system, what needed to be improved, and how they might envision an ideal guidance system. Since P4 is a co-author on this paper, we did not administer the SUS or semi-structured interview to him.

\hypertarget{results}{%
\section{Results and Discussion}\label{results}}
%%%

Fig.'s~\ref{fig:res-ul}-\ref{fig:res-full} plot the times needed to find the hotspot in both guidance conditions, and Fig.~\ref{fig:res-full} shows the raw times of each participant for each condition and hotspot. All times are in seconds; times reported as 120 secs. correspond to participants failing to find the target in the allotted time.

\begin{figure}
\includegraphics[width=12cm, keepaspectratio,]{res/img/hist.png}
\caption{
Histogram of the times to find the hotspots for each guidance condition, aggregated over participants and hotspots. The vertical dashed lines represent the median scores.}
\label{fig:res-ul}
\end{figure}

\begin{figure}
\includegraphics[width=12cm, keepaspectratio,]{res/img/lines.png}
\caption{
Line plot showing the average time to find the hotspot ($\pm{SE}$) per subject and per guidance condition.}
\label{fig:res-ur}
\end{figure}

\begin{figure}
\includegraphics[width=12cm, keepaspectratio,]{res/img/full.png}
\caption{
Time to find target hotspot location for each participant, colored by guidance condition. This plot displays all the raw experimental data.}
\label{fig:res-full}
\end{figure}

These plots show how the time to find the hotspot depends on factors such as the guidance condition (G vs. NG), the participant and which hotspot is the target. Note that G resulted in a successful target search in all cases, and in all but two cases (both for P4), target search took less time with G than with NG (visible in Fig. \ref{fig:res-full}).

We used a Wilcoxon signed-rank test to compare the differences between G and NG times (see Fig.~\ref{fig:res-diff}), paired by hotspot for each participant. The result indicated that participants performed significantly better under condition G (median = 14.5 sec.) than in condition NG (median = 120 sec.), with $V=5$, $Z=5.45$, $p = 5.18 \times 10^{-8}$, and an effect size of $r = 0.86$.

\begin{figure}[h!]
\includegraphics[width=11.5cm, keepaspectratio,]{res/img/hist_diff.png}
\caption{Histogram of the differences (paired by hotspot \& condition) in the time to find hotspots, aggregated over participants. Positive time differences indicate that the time under NG was longer than the time under G.}
\label{fig:res-diff}
\end{figure}

It should be noted that, despite our low number of participants, we had 10 pairs of measurements per participant, and a large effect-size (according to Cohen's guidelines), which should theoretically compensate for the increased type-I error rate risk inherent to running inferential statistics on a small sample.

The following System Usability Scale (SUS) scores were calculated: P1=65, P2=75, P3=77.5, for an average of 72.5. 
An SUS score of 68 is considered ``average'' while scores in the mid- to high 70s are considered ``good''\footnote{\url{https://measuringu.com/interpret-sus-score/}}.
Overall, the SUS scores suggest that the guidance system is usable but needs improvement.

Next we summarize the qualitative feedback we obtained in the semi-structured interviews. 
All participants who provided qualitative feedback (P1, P2 and P3) acknowledged the benefit of the audio guidance that was provided, which they found intuitive and clearly superior to finding hotspots without guidance, or to more indirect ways of providing guidance (such as the early version we implemented that used tempo to signal the distance from the target and pitch to direct the stylus up or down). P3 specifically favored the ``specific'' instructions that the verbal feedback provided to direct the user to a hotspot, which was especially useful when the hotspot was hard to find using tactile cues alone.

However, P1 and P2 felt that the limited spatial accuracy of the CamIO system was the biggest problem that needed to be addressed; for instance, in some cases the system announced the target had been reached even though the stylus tip was hovering about 1 cm above the truck surface. (This spatial inaccuracy
results from noise in the board pose and stylus tip location estimates.)
P3 expressed frustration with time lag, i.e., the voice feedback tended to lag behind the current location of the stylus, even when she was moving the stylus slowly; she also felt that the speed of the repetitive speech feedback made her feel rushed.

@@

We have devised a 3D spatial guidance system that helps a blind user find a specific location of interest on an object using CamIO, an audio-based AR system. 
The guidance system uses simple verbal commands (``left'', ``right'', ``up'', etc.) to tell the user which direction to
move the stylus tip. Experiments with four blind participants show that the guidance system significantly speeds up the search for target hotspots compared with an exhaustive search. 
A secondary contribution of this study is to demonstrate the ability of the CamIO stylus to access recessed or otherwise obscured locations on an object that are not themselves visible to the camera.

@@

\section{Acknowledgments}
JMC, BB and HS were supported by NIH grant 5R01EY025332 and NIDILRR grant 90RE5024-01-00. We thank Dr. Roberto Manduchi, Dr. Natela Shanidze, Dr. Santani Teng and Dr. Ali Cheraghi for helpful suggestions about the experiments.
